Notes on modeling for Kerr black holes: Basis learning, QNM frequencies, and spherical-spheroidal mixing coefficients

### 2018-06-18 docs/mvfits_paper/mvf.tex
updating doc

@@

  \cw_{\lmn} = m/2 + \kappa \sum_{j=1}^{J} c_j \kappa^k

@@

  \cw_{\lmn} = \sum_{j=0}^{J} c_j \kappa^k

@@

@@

% Equations for mixing coefficients
\begin{widetext}
  \input{src/ysprod_eqns}
\end{widetext}

% Plots of QNM frequencies
\begin{figure*}
  %
  \begin{tabular}{lcr}
    \includegraphics[width=\figfactor\textwidth]{fig/fits_w.pdf} & \includegraphics[width=\figfactor\textwidth]{fig/fits_tau.pdf}
  \end{tabular}
  %
	\caption{ Fits of dimensionless \qnm{} central frequencies (solid lines) along with select numerical values (grey markers) computed using Leaver's method \cite{Leaver85}.
  %
  Before the application of $\kappa(\j{})$, points are spaced between -\CwFitCalibrationRegion and \CwFitCalibrationRegion according to \CwFitCalibrationRegion times the $\sin$ of a fiducial angle which is uniformly spaced between $-\pi/2$ and $\pi/2$. Values of $\j{}$ are shown in the upper axis for $\kappa$ at $l=m$.
  %
  The grey dashed line marks the value of $\kappa$ where $\j{}=0$. Fits of dimensionless \qnm{} decay rates (solid lines) along with select numerical values (grey markers) computed using Leaver's method \cite{Leaver85}. }
  %
\end{figure*}

>>>>

% Plots of QNM frequencies
\begin{figure*}
  \begin{tabular}{lcr}
    \includegraphics[width=\figfactor\textwidth]{fig/fits_w.pdf} & \includegraphics[width=\figfactor\textwidth]{fig/fits_tau.pdf}
  \end{tabular}
	\caption{ Fits of dimensionless \qnm{} central frequencies (solid lines) along with select numerical values (grey markers) computed using Leaver's method \cite{Leaver85}.
  Before the application of $\kappa(\j{})$, points are spaced between -\CwFitCalibrationRegion and \CwFitCalibrationRegion according to \CwFitCalibrationRegion times the $\sin$ of a fiducial angle which is uniformly spaced between $-\pi/2$ and $\pi/2$. Values of $\j{}$ are shown in the upper axis for $\kappa$ at $l=m$.
  The grey dashed line marks the value of $\kappa$ where $\j{}=0$. Fits of dimensionless \qnm{} decay rates (solid lines) along with select numerical values (grey markers) computed using Leaver's method \cite{Leaver85}. }
  \label{fig:qnms}
\end{figure*}

@@

  \label{eq:zd}
  \cw_{\lmn} = m/2 + \kappa \sum_{j=1}^{J} c_j \kappa^k \; .

@@

  \label{eq:nzd}
  \cw_{\lmn} = \sum_{j=0}^{J} c_j \kappa^k \; .

@@

\par The polynomial content of \eqn{eq:zd} and \eqn{eq:nzd} is determined by \gmvp{}.
\eqns{eq:cw_fit_1}{eq:cw_fit_9} display the resulting polynomial models.
Although each model's fractional error is within 2\%, each is error is dominated by well known nonlinear oscillations which are considered to be outside of the experimental accuracy of current \gw{} efforts.
\par \fig{fig:qnms} displays select training points, as well as model fits for $\cw_{lmn}$'s real and imaginary parts.
For the right and left panels, simple polynomial behavior of each curve is a result of the displayed linear domain in $\kappa(\jf)$.
In the left panel, we have scaled $1/\tau_{\lmn}$ by factors for $m/(n+1/2)$ to place the \qnm{s} with $n=0$ and $n=1$ at approximately the same scale.

@@

\subsection{Modeling spherical-spheroidal inner-products using \gmvr{}}
% Equations for mixing coefficients
  \input{src/ysprod_eqns}
